### 2016-07-13 2016_Proceedings_ISMIR/keynotes.tex
big update of pre-defined pdfs from google docs, everything in place now except cover, need to finalize preface

%-------------------------------------------
\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Keynote Talks}
\includepdf[pages=1,pagecommand=\thispagestyle{empty}]{external/10_Keynotes.pdf}
\thispagestyle{empty}\cleardoublepage
 %-------------------------------------------
% Keynote talk 1
\addcontentsline{toc}{subsection}{Integrating Music Information Sources for Music Production and Consumption\\\textit{Mark Sandler}}
\includepdf[pagecommand=\thispagestyle{fancy}]{external/10-1_Keynotes-1.pdf}%

\thispagestyle{empty}\cleardoublepage
% Keynote talk 2
\addcontentsline{toc}{subsection}{The Promise of Music Information Retrieval: Are we there yet?\\\textit{J.\ Stephen Downie}}
\includepdf[pagecommand=\thispagestyle{fancy}]{external/10-2_Keynotes-2.pdf}%

>>>>

%-------------------------------------------
\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Keynote Talks}
\includepdf[pages=1,pagecommand=\thispagestyle{empty}]{external/10_Keynotes.pdf}
\thispagestyle{empty}\cleardoublepage
 %-------------------------------------------

% Keynote talk 1
\addcontentsline{toc}{subsection}{The New York Philharmonic Leon Levy Digital Archives: An Integrated View of Performance Since 1842\\\textit{Barbara Haws}}
\includepdf[pagecommand=\thispagestyle{fancy}]{external/10-1_Keynotes-1.pdf}%

\thispagestyle{empty}\cleardoublepage
% Keynote talk 2
\addcontentsline{toc}{subsection}{Is Machine Learning Enough?\\\textit{Beth Logan, PhD}}
\includepdf[pagecommand=\thispagestyle{fancy}]{external/10-2_Keynotes-2.pdf}%

### 2016-07-13 2016_Proceedings_ISMIR/tutorials.tex
big update of pre-defined pdfs from google docs, everything in place now except cover, need to finalize preface

%-------------------------------------------
\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Tutorials}
\includepdf[pages=1,pagecommand=\thispagestyle{empty}]{external/11_Tutorials.pdf}%
\thispagestyle{empty}\cleardoublepage
 %-------------------------------------------
% Tutorial 1
\includeabstract{Why Singing is Interesting}{Simon Dixon, Masataka Goto, Matthias Mauch}{external/11-1_Tutorial-1.pdf}

% Tutorial 2
\includeabstract{Addressing the Music Information Needs of Musicologists}{Richard J.\ Lewis, Ben Fields, Tim Crawford}{external/11-2_Tutorial-2.pdf}

% Tutorial 3
\includeabstract{Markov Logic Networks for Music Analysis}{Helene Papadopoulos}{external/11-3_Tutorial-3.pdf}

% Tutorial 4
\includeabstract{COmputation and FLAmenco: Why Flamenco is Interesting for
MIR Research}{Emilia G{\'o}mez, Nadine Kroher, Jose Miguel D{\'i}az-B{\'a}{\~n}ez, Sergio Oramas, Joaqu{\'i}n Mora, Francisco G{\'o}mez-Mart{\'i}n}{external/11-4_Tutorial-4.pdf}

% Tutorial 5
\includeabstract{Using Correlation Analysis and Big Data to Identify and Predict Musical Behaviors}{Jeff C.\ Smith}{external/11-5_Tutorial-5.pdf}

% Tutorial 6
\includeabstract{Automatic Music Transcription}{Zhiyao Duan, Emmanouil Benetos}{external/11-6_Tutorial-6.pdf}

>>>>

%-------------------------------------------
\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Tutorials}
\includepdf[pages=1,pagecommand=\thispagestyle{empty}]{external/11_Tutorials.pdf}%
\thispagestyle{empty}\cleardoublepage
 %-------------------------------------------

\newcommand{\includetut}[3]{\addcontentsline{toc}{subsection}{#1\\\textit{#2}}
\includepdf[pages=#3, pagecommand=\thispagestyle{fancy}]{external/11_TutorialsAll.pdf}}

% Tutorial 1
\includetut{Jazz solo analysis between music information
  retrieval, music psychology, and jazz research}{Jakob Abe{\ss}er,
  Klaus Frieler, Wolf-Georg Zaddach}{1-2}

% Tutorial 2
\includetut{Music Information Retrieval: Overview, Recent
  Developments and Future Challenges}{Emilia G\'omez, Markus Schedl,
  Xavier Serra, Xiao Hu}{3}

% Tutorial 3
\includetut{Why is studio production interesting?}{Emmanuel
Deruty, Fran\c{c}ois Pachet}{4-5}

% Tutorial 4
\includetut{Introduction to EEG Decoding for Music Information Retrieval
Research}{Sebastian Stober, Blair Kaneshiro}{6}

% Tutorial 5
\includetut{Natural Language Processing for MIR}{Sergio Oramas,
  Luis Espinosa-Anke, Shuo Zhang, Horacio Saggion}{7}

% Tutorial 6
\includetut{Why Hip-Hop is interesting}{Jan Van Balen, Ethan
  Hein, Dan Brown}{8-9}
